Benchmarking on Rigetti architecture

### 2022-10-05 txt/manuscript.tex
circuit drawings
Add pictures of circuits in Section 4.

\subsection{Native case}

@@

@@

@@

>>>>

\subsection{Generic case}
Now we present the circuits for the generic case.
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-None}
\caption{Circuit representing state preparation in the  generic case.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-None}
\caption{Circuit representing $U^\dagger$ in the generic case.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-None}
\caption{Circuit representing $V_0^\dagger$ in the generic case.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-None}
\caption{Circuit representing controlled $V_0$ and $V_1$ the generic case.}
\end{figure}

\subsection{IBMQ and Lucy}

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-ibmq}
\caption{Circuit representing state preparation for IBMQ.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-ibmq}
\caption{Circuit representing $U^\dagger$ for IBMQ.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-ibmq}
\caption{Circuit representing $V_0^\dagger$ for IBMQ.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-ibmq}
\caption{Circuit representing controlled $V_0$ and $V_1$ for IBMQ.}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-lucy}
\caption{Circuit representing state preparation for Lucy.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-lucy}
\caption{Circuit representing $U^\dagger$ for Lucy.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-lucy}
\caption{Circuit representing $V_0^\dagger$ for Lucy.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-lucy}
\caption{Circuit representing controlled $V_0$ and $V_1$ for Lucy.}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/state_preparation-rigetti}
\caption{Circuit representing state preparation for Rigetti.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/u_dag-rigetti}
\caption{Circuit representing $U^\dagger$ for Rigetti.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/v0_dag-rigetti}
\caption{Circuit representing $V_0^\dagger$ for Rigetti.}
\end{figure}
\begin{figure}[h!]
\centering
\includegraphics[scale=1.8]{pics/circuit-qiskit/controlled_v0_v1_dag-rigetti}
\caption{Circuit representing controlled $V_0$ and $V_1$ for Rigetti.}
\end{figure}
